Mamba vs SOTA for Vision Tasks\\ \thanks{$\dagger$ Equal contributions}

### 2024-04-30 paper/main.tex
rearrange

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{caption} % for caption setup

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{caption} 
\usepackage{afterpage}

@@

\appendix

\subsection{Supplementary Figures} \label{supp_figs}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/14_9.png}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/22_4.png}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/13_4.png}
    \caption{In some cases, such as this one, it was observed that models with too few parameters (UltraLight-VM-UNet, UltraLight-VM-UNet-v2) don't detect sections of the tumor during segmentation.}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/19_4.png}
    \caption{UltraLight-VM-UNet-v5 achieved segmentation results equivalent to UMambaBot with approximately 9.1 M less parameters.}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/0_0.png}
    \caption{An example of models with pyramidal pooling in the PVM blocks (UltraLight-VM-UNet-v4, UltraLight-VM-UNet-v6) achieved an improvement over a model without (UltraLight-VM-UNet-v5).}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/12_2.png}
\end{figure*}
\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/22_3.png}
\end{figure*}
\begin{figure*}[!h]
    \centering
    \includegraphics[width=\textwidth]{imgs/22_7.png}
\end{figure*}
